Anonymous provision of services via blockchain

### 2021-12-29 main.tex
update state of the art

Such user information can be used then for commercial gains. For example, by reselling it to marketers, other businesses or even cybercriminals. Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance ~\cite{}

>>>>

Such user information can be then used deliberately or unintentionally (e.g, by theft) for: insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, finantial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.
